Project Overview

### 2022-05-06 doc/overview_document.tex
Added a script to work on emmean se plots

---
title: "Project Overview"
author: "Jay Gillenwater"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## target knits Rmds in their own session, so load libraries here.
source(here::here("packages.R"))
```

```{r load-targets, include=FALSE}
tar_load(c(pop_development_pdf))
```

## Introduction

This document is a high-level overview of the experimental design and objectives of the "Jay" yield tests.

## Objectives

@@

## Experimental design

@@

## Population development

@@

```{r pop_flowchart, echo = FALSE, warning=FALSE, fig.align="center"}

knitr::include_graphics(pop_development_pdf)
```

## Collected data

@@

## Analysis and questions

@@

$$y = \mu + GEN + ENV + GEN:ENV + REP(ENV) + \epsilon$$

Where y is the value of some phenotype, $\mu$ is the overall mean, GEN is the genotype effect, ENV is the environment effect, GEN:ENV is the genotype x environment interaction effect, REP(ENV) is the effect of replication nested within environment, and $\epsilon$ is the measurement error. This model was used to perform an analysis of variance and to obtain genotype least square means.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Project Overview},
  pdfauthor={Jay Gillenwater},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Project Overview}
\author{Jay Gillenwater}
\date{06 May, 2022}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

This document is a high-level overview of the experimental design and
objectives of the ``Jay'' yield tests.

\hypertarget{objectives}{%
\subsection{Objectives}\label{objectives}}

@@

\hypertarget{experimental-design}{%
\subsection{Experimental design}\label{experimental-design}}

@@

\hypertarget{population-development}{%
\subsection{Population development}\label{population-development}}

@@

\begin{center}\includegraphics{C:/Users/Jay/Desktop/Documents/R/Jay_yield/exports/plots/pop_development_flowchart} \end{center}

\hypertarget{collected-data}{%
\subsection{Collected data}\label{collected-data}}

@@

\hypertarget{analysis-and-questions}{%
\subsection{Analysis and questions}\label{analysis-and-questions}}

@@

\[y = \mu + GEN + ENV + GEN:ENV + REP(ENV) + \epsilon\]

Where y is the value of some phenotype, \(\mu\) is the overall mean, GEN
is the genotype effect, ENV is the environment effect, GEN:ENV is the
genotype x environment interaction effect, REP(ENV) is the effect of
replication nested within environment, and \(\epsilon\) is the
measurement error. This model was used to perform an analysis of
variance and to obtain genotype least square means.

@@

\end{document}
